\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{tgpagella}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  bottom=13mm,
  top=13mm
}

\pagestyle{empty}

\newcommand{\firstname}{Martim}
\newcommand{\lastname}{Silva}

%%%%%%%%%%%%% Colors %%%%%%%%%%%%%

\definecolor{nokiaBlue}{HTML}{2563EB}
\definecolor{grayShy}{RGB}{153, 150, 142}

\newcommand{\mainColor}{nokiaBlue}

%%%%%%%%%%%%% Spaces %%%%%%%%%%%%%

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% Horizontal %

\newcommand{\xhspace}{\hspace*{0.1em}}
\newcommand{\shspace}{\hspace*{0.8em}}

% Vertical %

\newcommand{\xvspace}{\vspace*{0.1em}}
\newcommand{\svspace}{\vspace*{0.5em}}
\newcommand{\mvspace}{\vspace*{1.5em}}
\newcommand{\hvspace}{\vspace*{2.5em}}

\newcommand{\negxvspace}{\vspace*{-0.2em}}
\newcommand{\negsvspace}{\vspace*{-0.5em}}
\newcommand{\negmvspace}{\vspace*{-1em}}
\newcommand{\neghvspace}{\vspace*{-1.5em}}

%%% Personal Details Macro %%%

\newcommand{\userInfo}[4]{
    \begin{flushleft}
        \color{\mainColor}
        \Huge
        \textbf{\MakeUppercase{\lastname}}
        \color{black}
        \textbf{\firstname}
        \color{\mainColor}
        \noindent\rule{19.1cm}{0.8pt}
        \color{grayShy}
        \small
        \par
        \parbox{7\spacebox} {
            \faMap \shspace #1 - #2 \par \svspace
            \faPhone \shspace #3 \par \svspace
            \faEnvelopeOpen \shspace \texttt{#4} \par \svspace
        }
        \color{\mainColor}
        \mvspace
    \end{flushleft}
    \negmvspace
}

%%% Company Details Macro %%%

\newcommand{\companyInfo}[4]{
    \begin{flushright}
        \parbox{4\spacebox}{
            \raggedleft
            \small
            \textbf{\today}\par
            \xvspace
            \textbf{#1}\par
            \mvspace
            \color{grayShy} \textsc{\MakeLowercase{#2}}\par
            \xvspace
            \textsc{\MakeLowercase{#3}}\par
            \xvspace
            \textsc{\MakeLowercase{#4}}\par
            \color{black}
        }
    \end{flushright}
    \hvspace
}

%%% RE Macro %%%

\newcommand{\object}[1]{
    \small
    \color{\mainColor} \textbf{RE :} \color{black} \textbf{#1} \par
}

%%% Content Macro %%%

\newcommand{\content}[2]{
    \mvspace
    \begin{flushleft}
        \parbox{10.3\spacebox}{
          #1\par
          \svspace
          #2
        }\par
    \end{flushleft}
}

%%% Signature Macro %%%

\newcommand{\signature}{
    \svspace
    \parbox{3\spacebox}{
      Sincerely,\par
      \svspace \hspace{-0.3em}
      \textbf{\color{\mainColor} \firstname\ \MakeUppercase{\lastname}}\par
      \svspace \svspace
      \Huge \faPenNib\par
    }\par
}

%%%%%%%%%%%% Cover Letter %%%%%%%%%%%%

\begin{document}
\fontfamily{phv}\selectfont
\userInfo{Lisbon}{Portugal}{+351 936 495 912}{Martim.Alexandre.Dras@gmail.com}
\companyInfo{Nokia}{Talent Acquisition Team}{Amadora}{Portugal}
\object{Cloud Infrastructure Trainee -- Portugal (Hybrid)}
\content{
  Dear Nokia Talent Acquisition Team, \\

  I am applying for the Cloud Infrastructure Trainee position in Nokia Portugal. The importance
  of Nokia's contribution to next-generation telecom infrastructure is relevant to my academic
  curriculum, and I am eager to join a team that is working to develop innovative cloud and
  automation solutions. \\

  Through my studies at ISEL, I have gained practical exposure to the technologies required
  for this position. As part of my Network Automation and Orchestration course, I deployed
  and automated a multi-vendor lab environment with \textbf{Nokia SR Linux}, Arista cEOS,
  and Mikrotik RouterOS using \textbf{Ansible}, Jinja2 templates, NAPALM, and Netmiko.
  This project allowed me to familiarize myself with Nokia's network OS and the
  template-based onboarding process mentioned in this job description. I expanded upon this
  by building a telemetry system using \textbf{gNMI}, Prometheus, and Grafana metrics,
  combined with a GitHub Actions CI/CD pipeline for validating changes before deployment.
  Simultaneously, I am creating embedded firmware for a PocketQube satellite using FreeRTOS
  and Python. \\

  I am currently located in Lisbon, available to begin immediately, and am flexible working
  in a hybrid environment. It would be my pleasure to discuss how my qualifications align
  with this position. \\
}{Sincerely,}
\signature
\end{document}
