\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{tgpagella}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  bottom=13mm,
  top=13mm
}

\pagestyle{empty}

\newcommand{\firstname}{Martim}
\newcommand{\lastname}{Silva}

%%%%%%%%%%%%% Colors %%%%%%%%%%%%%

\definecolor{nokiaBlue}{HTML}{2563EB}
\definecolor{grayShy}{RGB}{153, 150, 142}

\newcommand{\mainColor}{nokiaBlue}

%%%%%%%%%%%%% Spaces %%%%%%%%%%%%%

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

\newcommand{\xhspace}{\hspace*{0.1em}}
\newcommand{\shspace}{\hspace*{0.8em}}

\newcommand{\xvspace}{\vspace*{0.1em}}
\newcommand{\svspace}{\vspace*{0.5em}}
\newcommand{\mvspace}{\vspace*{1.5em}}
\newcommand{\hvspace}{\vspace*{2.5em}}

\newcommand{\negxvspace}{\vspace*{-0.2em}}
\newcommand{\negsvspace}{\vspace*{-0.5em}}
\newcommand{\negmvspace}{\vspace*{-1em}}
\newcommand{\neghvspace}{\vspace*{-1.5em}}

\newcommand{\userInfo}[4]{
    \begin{flushleft}
        \color{\mainColor}
        \Huge
        \textbf{\MakeUppercase{\lastname}}
        \color{black}
        \textbf{\firstname}
        \color{\mainColor}
        \noindent\rule{19.1cm}{0.8pt}
        \color{grayShy}
        \small
        \par
        \parbox{7\spacebox} {
            \faMap \shspace #1 - #2 \par \svspace
            \faPhone \shspace #3 \par \svspace
            \faEnvelopeOpen \shspace \texttt{#4} \par \svspace
        }
        \color{\mainColor}
        \mvspace
    \end{flushleft}
    \negmvspace
}

\newcommand{\companyInfo}[4]{
    \begin{flushright}
        \parbox{4\spacebox}{
            \raggedleft
            \small
            \textbf{\today}\par
            \xvspace
            \textbf{#1}\par
            \mvspace
            \color{grayShy} \textsc{\MakeLowercase{#2}}\par
            \xvspace
            \textsc{\MakeLowercase{#3}}\par
            \xvspace
            \textsc{\MakeLowercase{#4}}\par
            \color{black}
        }
    \end{flushright}
    \hvspace
}

\newcommand{\object}[1]{
    \small
    \color{\mainColor} \textbf{RE :} \color{black} \textbf{#1} \par
}

\newcommand{\content}[2]{
    \mvspace
    \begin{flushleft}
        \parbox{10.3\spacebox}{
          #1\par
          \svspace
          #2
        }\par
    \end{flushleft}
}

\newcommand{\signature}{
    \svspace
    \parbox{3\spacebox}{
      Sincerely,\par
      \svspace \hspace{-0.3em}
      \textbf{\color{\mainColor} \firstname\ \MakeUppercase{\lastname}}\par
      \svspace \svspace
      \Huge \faPenNib\par
    }\par
}

%%%%%%%%%%%% Cover Letter %%%%%%%%%%%%

\begin{document}
\fontfamily{phv}\selectfont
\userInfo{Lisbon}{Portugal}{+351 936 495 912}{Martim.Alexandre.Dras@gmail.com}
\companyInfo{Nokia}{Talent Acquisition Team}{5G Layer 1 Software}{Amadora, Portugal}
\object{SW Engineer Trainee -- 5G Layer 1 (Amadora)}
\content{
  Dear Nokia Talent Acquisition Team, \\

  I'm writing you today to apply for a Software Engineer Trainee at Nokia, in the
  5G Layer 1 Software team, located in Amadora. \\

  Developing embedded software for 5G base stations running in hard real-time
  conditions is precisely the field I wish to enter in. \\

  Working in Nokia's L1 team in this field would be very motivational and
  interesting for me. \\

  My previous experience is highly compatible with this role. For my PocketQube
  satellite development project at ISEL, I developed \textbf{FreeRTOS}-based
  firmware in \textbf{C/C++} for an embedded SoC working under hard real-time
  constraints; including implementing interrupt-driven task scheduling, interrupt
  handling, and telemetry. My experience in cross-compilation toolchains,
  hardware-in-the-loop simulation, and \textbf{Python}-based embedded workflows is
  also relevant for the job description. At the same time, my Network Automation
  project employs the exact same DevOps/Docker/CI stack, namely, GitHub Actions
  \textbf{CI/CD}, and ContainerLab on \textbf{Linux}. Moreover, three years of
  development in embedded C/C++ on Arduino microcontrollers in multiple robotics
  competition teams (First Global Geneva, European RoboCup, CanSat, Robótica)
  helped me lay a foundation in real-time embedded software development, which I
  continue to apply in more complex scenarios. \\

  I'm set to graduate my BSc in Informatics, Networks, and Telecommunications
  Engineering in July 2026. That makes the position's requirement of April 2026
  very compatible with my schedule. I am based in Lisbon, and ready to work in
  Nokia offices in Amadora. \\
}{Sincerely,}
\signature
\end{document}
