\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{tgpagella}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  bottom=13mm,
  top=13mm
}

\pagestyle{empty}

\newcommand{\firstname}{Martim}
\newcommand{\lastname}{Silva}

%%%%%%%%%%%%% Colors %%%%%%%%%%%%%

\definecolor{feedzaiRed}{HTML}{C8102E}
\definecolor{grayShy}{RGB}{153, 150, 142}

\newcommand{\mainColor}{feedzaiRed}

%%%%%%%%%%%%% Spaces %%%%%%%%%%%%%

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

\newcommand{\xhspace}{\hspace*{0.1em}}
\newcommand{\shspace}{\hspace*{0.8em}}

\newcommand{\xvspace}{\vspace*{0.1em}}
\newcommand{\svspace}{\vspace*{0.5em}}
\newcommand{\mvspace}{\vspace*{1.5em}}
\newcommand{\hvspace}{\vspace*{2.5em}}

\newcommand{\negxvspace}{\vspace*{-0.2em}}
\newcommand{\negsvspace}{\vspace*{-0.5em}}
\newcommand{\negmvspace}{\vspace*{-1em}}
\newcommand{\neghvspace}{\vspace*{-1.5em}}

\newcommand{\userInfo}[4]{
    \begin{flushleft}
        \color{\mainColor}
        \Huge
        \textbf{\MakeUppercase{\lastname}}
        \color{black}
        \textbf{\firstname}
        \color{\mainColor}
        \noindent\rule{19.1cm}{0.8pt}
        \color{grayShy}
        \small
        \par
        \parbox{7\spacebox} {
            \faMap \shspace #1 - #2 \par \svspace
            \faPhone \shspace #3 \par \svspace
            \faEnvelopeOpen \shspace \texttt{#4} \par \svspace
        }
        \color{\mainColor}
        \mvspace
    \end{flushleft}
    \negmvspace
}

\newcommand{\companyInfo}[4]{
    \begin{flushright}
        \parbox{4\spacebox}{
            \raggedleft
            \small
            \textbf{\today}\par
            \xvspace
            \textbf{#1}\par
            \mvspace
            \color{grayShy} \textsc{\MakeLowercase{#2}}\par
            \xvspace
            \textsc{\MakeLowercase{#3}}\par
            \xvspace
            \textsc{\MakeLowercase{#4}}\par
            \color{black}
        }
    \end{flushright}
    \hvspace
}

\newcommand{\object}[1]{
    \small
    \color{\mainColor} \textbf{RE :} \color{black} \textbf{#1} \par
}

\newcommand{\content}[2]{
    \mvspace
    \begin{flushleft}
        \parbox{10.3\spacebox}{
          #1\par
          \svspace
          #2
        }\par
    \end{flushleft}
}

\newcommand{\signature}{
    \svspace
    \parbox{3\spacebox}{
      Sincerely,\par
      \svspace \hspace{-0.3em}
      \textbf{\color{\mainColor} \firstname\ \MakeUppercase{\lastname}}\par
      \svspace \svspace
      \Huge \faPenNib\par
    }\par
}

%%%%%%%%%%%% Cover Letter %%%%%%%%%%%%

\begin{document}
\fontfamily{phv}\selectfont
\userInfo{Lisbon}{Portugal}{+351 936 495 912}{Martim.Alexandre.Dras@gmail.com}
\companyInfo{Feedzai}{Hiring Team}{Risk Engine Platform}{Portugal}
\object{Software Engineer -- Product (Risk Engine)}
\content{
  Dear Feedzai Hiring Team, \\

  I am writing regarding the Software Engineer position on the Risk Engine team.
  Real-time fraud detection running on distributed, cloud-native infrastructure
  under strict latency constraints is exactly the kind of engineering I want to
  grow into, and Feedzai's reputation for engineering excellence and the
  ``you build it, you run it'' ownership mindset is what draws me to this team. \\

  My experience comes from adjacent domains. My ongoing Network Automation lab at
  ISEL is a multi-vendor \textbf{distributed} environment orchestrated in
  \textbf{Python} with Ansible and \textbf{ContainerLab}, instrumented with a
  gNMI + \textbf{Prometheus} + Grafana observability stack and a GitHub Actions
  \textbf{CI/CD} pipeline -- end-to-end ownership from code to deployment. At
  YEPKIT, I developed and containerised \textbf{backend} services in \textbf{Node.js}
  with \textbf{Docker}, contributing to REST API design and modular structure. In
  parallel, my PocketQube satellite project has me writing real-time
  \textbf{C/C++} firmware under hard latency constraints, sharpening the systems
  thinking that translates to high-performance backend work. \\

  I am based in Lisbon and available to begin immediately. I would welcome the
  opportunity to discuss how my background, curiosity, and trajectory can fit
  Feedzai's team. \\
}{Sincerely,}
\signature
\end{document}
